\vspace{-3em} \includegraphics[width=.1\textwidth]{Figures/logo.png} \\ \includegraphics[width=4cm]{Figures/datarea.pdf} \\

### 2014-10-02 report/article_4.tex
logo swap, colour change

%% additional packages:
\usepackage{wrapfig}
\usepackage[left=1.2in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{caption}

@@

\title{ \vspace{-3em}
\includegraphics[width=5cm]{Figures/datarea.pdf} \\
{\large \#SummerDataChallenge}} % The article title

\author{ {\large Benjamin L. Moore\textsuperscript{1}}} % The article author(s) - author affiliations need to be specified in the AUTHOR AFFILIATIONS block

@@

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I employed \emph{ARIMA forecasting}
to extrapolate an area's price trend with an eye to suggesting
profitable investments. Finally, these and other metrics were combined
into an \emph{investment grade} for a given postcode area. Combined
this set of analyses forms the basis of \logo, a product aimed at
``democratising real estate investment'', offering individuals and
businesses quantitative real estate insights for data-driven investment
decisions.

@@

\section{Description of analyses}

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
\begin{center}
\includegraphics[width=.44\textwidth]{Figures/fractal.png}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=.9\textwidth]{Figures/arima.png}
\caption{Example ARIMA forecast of median house prices for a specific postcode.}
\end{center}
\end{figure}

>>>>

%% additional packages:
\usepackage{wrapfig}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{caption}

@@

\title{ \vspace{-3em}
\includegraphics[width=.1\textwidth]{Figures/logo.png} \\
\includegraphics[width=4cm]{Figures/datarea.pdf} \\
} % The article title

\author{  Summer data challenge entry by Benjamin
  L. Moore\textsuperscript{1} } % The article author(s) - author affiliations need to be specified in the AUTHOR AFFILIATIONS block

@@

I analysed the {\bf London house prices} dataset is several innovative
ways. Firstly \emph{fractal context} shows how house sales within an
arbitrary area relate to those if neighbouring districs, up and down
the postcode hierarchy. Secondly, I fit \emph{ARIMA models} to
forecast an area's price trend into the future, with an eye to
suggesting profitable investments. Finally, these and other metrics
were combined into an \emph{investment grade} for a given postcode
area. Combined this set of analyses forms the basis of \logo, a
product aimed at ``democratising real estate investment'', offering
individuals and businesses quantitative real estate insights for
data-driven investment decisions.

@@

\section*{Description of analyses}

@@

\setlength{\intextsep}{0em}
\begin{wrapfigure}{R}{.45\textwidth}
\begin{center}
\includegraphics[width=.44\textwidth]{Figures/fractal.pdf}
\caption{ Fractal context of postcode SW18 4HU in Wandsworth, South London.}
\end{center}
\end{wrapfigure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=.9\textwidth]{Figures/arima.pdf}
\caption{Example ARIMA forecast of median house prices for a specific postcode.}
\end{center}
\end{figure}
